%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Document is an article for a4 paper
\documentclass[a4paper]{article}
%% Encoding is utf8
\usepackage[utf8]{inputenc}
%% Fonts
\usepackage[T1]{fontenc}
%% Include graphic.
\usepackage{graphicx}
%% Use PGF to draw.
\usepackage{tikz}
%% Use tabularx
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{array}
%% Babel package
\usepackage[english]{babel}
%% Bit fields: to create message descriptions
\usepackage[bitheight=6ex]{bytefield}
%% Use hyper reference.
\usepackage[bookmarksopen=true]{hyperref}
\hypersetup{%
pdftitle={Configuration Library},
pdfauthor={Anthony Jaguenaud},
pdfsubject={Configuration library},
pdfkeywords={}}
%% Setup links.
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.3,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkbrown}{rgb}{0.28,0.07,0.07}

\hypersetup{%
  colorlinks=true,
  citecolor=darkblue,
  urlcolor=darkgreen,
  linkcolor=darkred,
  menucolor=darkbrown}

\begin{document}

 \tableofcontents
 \section{Goals}
 \begin{abstract}
   Goal of this software, is to create a “config” class in a generated library.
 \end{abstract}

  When developer need to store how its application or library does work, he needs some configuration files.
 There is lots of format for configuration files : \emph{ini}, \emph{xml}, \emph{Windows register} \dots

 Lots of time, the configuration is delegated to software by library. For example, I have a library for encode movies. My library needs lots of information, like : encoding format,
 frame rate \dots
 But, two applications can use my library. If configuration is delegate to library, all the two applications will inherit of same configuration. So applications make configuration.
 The problem in this case, is that applications need to redevelop a configuration parsing with work duplicated, and possibility of mistakes.

 Lots of configuration files have diferents format and no one application to edit them.

 Configuration files have parsed with parsing libraries, so you have to create a better API to use your configuration. Some times an administrator can authorized users to have their own
 config, or only some fields.

 This project goal is to create a software that with an input file describing configuration, is going to generate a C++ class for read configuration, generate an API documentation of this
 class.
 An other goal, is to generate a Qt application that can create configuration of every compiled class.

 \section{Inputs and Outputs}
 \begin{abstract}
   This is global conception part.
 \end{abstract}

 \subsection{Inputs}
 \subsection{Outputs}
 \section{Generator}
 \section{API generated}
\end{document}
